No-click browsing of large hierarchical data

### 2020-05-26 paper/HCC2020-short/paper.tex
Short論文化したもの

\long\def\ttt#1{\texttt{\small #1}}
\long\def\tsf#1{\textsf{\small{#1}}}
\long\def\tit#1{\textit{\small{#1}}}

@@

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

@@

\begin{abstract}
We introduce a novel simple interaction technique for finding and browsing
data in a huge hierarchical database using only two keys.

Finding a data from a huge hierarchical database takes time
because users should traverse the tree using a mouse or a keyboard,
and click a ``select'' button to check the content.
If the data was not appropriate,
he should go to the next entry and perform the selection task again.

In the past, when only a small number of ``channels'' were available
from broadcast TV stations, users could simply rotate
a television dial to select a channel and watch the program.
We introduce a simple interaction technique called ``Gear'',
with which users can select an entry from a large hierarchical database and
browse it instantly, just like we could select a channel and enjoy a program
using old television dials.
\end{abstract}

@@

Huge amount of movies, musics, and other programs are available on the web, but
finding and viewing a program is not easy because
(1) finding a program takes time, and
(2) a ``confirm'' operation (clicking something or typing a key)
is required for viewing the content.

% 昔のテレビやラジオではこの手間がなかった
% チャンネルやチューニングつまみを回すだけでよかった
% 選択操作はなかった
% つまりいわゆる「ザッピング」が可能であった

The confirm operations was not required on old TVs and radios,
because we could enjoy TV/radio programs
as soon as we rotated a TV channel dial or a tuning dial of the radio.

\begin{figure}[H]
\centerline{
   \includegraphics[width=35mm,bb=0 0 279 272]{figures/9bd96506bdaac48b26c5cd192851c11d.png}
   \includegraphics[width=35mm,bb=0 0 128 72]{figures/fedc4f3c899c48b5a3ddd0982801c79d.png}
}
\caption{An old TV channel dial and a radio tuning dial}
\label{TV channel}
\end{figure}

% 一般に、選択するとすぐに見えるのはどこでも便利なものである
% Finderのカバーフローや、最下層では選択内容がすぐに見えたりする
% このときはConfirmの手間なく内容を見られるのは便利なもので、
% これをno-click browsingと呼ぶことにする
% TVもラジオもno-click browsingが可能であった

It is always convenient to view the contents of the selected item
as soon as we find it.
We call such viewing style as ``\textbf{\tit{no-click browsing}}''.

We can use the no-click browsing style on personal computers.
Using the Finder.app on MacOS, we can use the ``Cover Flow''\footnote{
  \tsf{https://en.wikipedia.org/wiki/Cover\_Flow}
} viewer to browse the contents in a folder
with simple swiping gestures (Figure \ref{coverflow}).

\begin{figure}[H]
\centerline{\includegraphics[width=65mm,bb=0 0 1080 740]{figures/902678c6770b5e043baa6f503375749f.jpg}}
% \centerline{\includegraphics[width=80mm,bb=0 0 803 555]{figures/5d46fb09c3c5b4baccfd68ca026ef25b.png}} % Monorail
\caption{Cover Flow on MacOS}
\label{coverflow}
\end{figure}

We can also enjoy no-click browsing on the ``column view'' mode of Finder.app.
In the column view mode, 
the contents of the file is shown at the right side of the window
as soon as we select a file in a folder (Figure \ref{noclickfinder}).
When we type an arrow key and select another file,
the contents is shown instantly without a confirm operation.

\begin{figure}[H]
% \centerline{\includegraphics[width=70mm,bb=0 0 1678 846]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
\centerline{\includegraphics[width=70mm,bb=0 0 839 423]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
\caption{No-click browsing on the ``column view'' of Finder.app.}
\label{noclickfinder}
\end{figure}

% テレビやカバーフローのザッピングはもちろんソースが少なかったからできるわけだが、
% 大量データの場合はこれが難しい。
% 何千個もソースがある場合は
% 階層をたどる処理が必要になり、その移動操作が必要だからである

@@

% 階層でもそうでなくても、移動操作は慣れている
% 適切な階層構造を用意して、クリックしながらたどるのがブラウザでは一般的である
% ブラウザの場合、カバーフローのようなインタフェースは一般的でないので、
% みつけたものを選択したり戻ったりを繰り返さなければならない。
% 
% ブラウザでは階層のInfoVis[]もいろいろあるが、操作に頭を使うし、no-clickブラウジングできるものは無い。

% 階層的なら上下操作でなんとかなる
% 小型機器で階層情報をたどるときは4-wayでひとつずつたどるのが普通

% The simplest way of navigatin a hierarchical data is to use four keys

When a user cannot use a pointing device,
key-based interaction techniques are used for
finding information in hierarchical data.
%
For example, a user can find a music data by
selecting an artist from the list of artist names,
selecting an album title from the title list,
and selecting a music title from the song list.
%
Users can use two keys for choosing an entry from the list
% (e.g. selecting an artist from the artist list),
and use another key for selecting an entry and moving to the next level.
% (e.g. selecting an artist and show album titles).
It is also necessary to use another key for going back to the previous level.
% (e.g. showing the artist list for artist selection).
This 4-way navigation is popular on small devices
and remote controllers for selecting a song from the hierarchical data.
4-way navigation is also available on the column view of Finder.app.

\begin{figure}[H]
\centerline{
  \includegraphics[width=30mm,bb=0 0 333 250]{figures/0048a5e91ddcf1d5670bd958e3c55619.jpg}
  \includegraphics[width=30mm,bb=0 0 551 551]{figures/70c036b24525c6cace9955b24152e97e.jpg}
  }
\caption{Small devices supporting 4-way navigation}
\label{rio}
\end{figure}

Using 4 keys might be okay on these devices, but it would be better
if we could perform the navigation task using simpler devices that have only two keys.
In that case, we can use a rotating device like a disk or a wheel for the navigation,
since such devices can generate two signals based on the rotation direction.

We have developed a new navigation technique called ``{Gear}'' for no-click browsing,
where users can explore a large hierarchical database by using only two keys.

@@

Interaction with Gear is based on the following simple principles.
Two types of operations,
{\up} (up) and {\down} (down), are used for the navigation.
They can be performed either by pressing keys or rotating a dial.

@@

\begin{figure}[H]
% \includegraphics[width=70mm]{figures/fig1.pdf}
\centerline{\includegraphics[width=70mm,bb=0 0 490 490]{figures/fig1.pdf}}
\caption{Sample data: shops data of a shopping mall.}
\label{fig1}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=\menuwidth, bb=0 0 139 157]{figures/fig2.pdf}}
\caption{Initial display.}
\label{fig2}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 157]{figures/fig3.pdf}}
\caption{Typing {\down}.}
\label{fig3}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 157]{figures/fig4.pdf}}
\caption{Selecting Food/drink.}
\label{fig4}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 238]{figures/fig5.pdf}}
\caption{Selecting Liquor shop.}
\label{fig5}
\end{figure}

When the user issues {\down} twice here,
\tsf{Fresh grocery} category is selected (Figure \ref{fig6}).

\begin{figure}[H]
\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 238]{figures/fig6.pdf}}
\caption{Selecting Fresh grocery.}
\label{fig6}
\end{figure}

If the user keeps issuing {\down}, 
the list will change to Figure \ref{fig8},
without expanding the children of \tsf{Fresh grocery}.

\begin{figure}[H]
\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 157]{figures/fig8.pdf}}
\caption{Selecting Clothing.}
\label{fig8}
\end{figure}

If the use stops issuing {\down} at Figure \ref{fig6},
the shops under category \tsf{Fresh grocery} is automatically selected (Figure \ref{fig7}).

\begin{figure}[H]
\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 292]{figures/fig7.pdf}}
\caption{Selecting Fish store.}
\label{fig7}
\end{figure}

When the user issues {\up} here, \tsf{Fresh grocery} is selected,
and the shops under \tsf{Fresh grocery} disappears, 
resulting in the same state as Figure \ref{fig6}.
If the user issues {\up} two more times, the display changes to the state
shown in Figure \ref{fig5},
and one more {\up} will set the system to the state of Figure \ref{fig4}.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=\menuwidth,bb=0 0 139 211]{figures/fig9.pdf}}
\caption{Selecting Shoes store.}
\label{fig9}
\end{figure}

@@

% SerencastというサービスでGearを使う
% SerencastはScrapboxを利用したものである

To prove that Gear is useful for selecting an entry from a
large hierarchical database,
we have developed the ``\tsf{\SC}'' service, where
users can enjoy movies, musics, and other web services
on the browser with the Gear interface without selecting (clicking) an item.
{\SC} is implemented in JavaScript, and runs on modern web browsers

{\SC} uses the ``\tsf{\SB}'' wiki service\footnote{
  \tsf{https://Scrapbox.io/}
} for listing the contents of the hierarchical database.
{\SB} is an interactive wiki
system where users can share and edit texts on the web browser.
A user can create a {\SB} ``project'', and create pages
that consists of texts and links.
People can share the page and edit it interactively on their browsers
just like the Google Docs system\footnote{
  \tsf{https://www.google.com/docs/about/}
}.

\begin{figure}[H]
\centerline{\includegraphics[width=75mm,bb=0 0 1553 1174]{figures/28818d749896f87f3eb8bd6b6f9e9a36.png}}
\caption{An example of a {\SB} project.}
\label{exampleproject}
\end{figure}

Figure \ref{exampleproject} shows an example of a {\SB} project.
The title of the project is ``Scrapbox help'', and
other pages like ``Features'' exist in the project.

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 1606 1200]{figures/9e867c325bafc415bd0870c1717fbaf7.png}}
\caption{An example {\SB} page.}
\label{examplepage}
\end{figure}

Figure \ref{examplepage} is an example of a {\SB} page.
%
The page is based on plain text just like an WikiPedia page is based on plain text.
Users can use special markup tags
like ``\texttt{[}'' and ``\texttt{]}'' to show bold texts, icons, URL links,
and links to other pages.
In this example, a URL link to {\tsf{http://gyazo.com}} is used
just like an \tsf{A} tags in HTML.

The raw text of the {\SB} page looks like this:

{\scriptsize
\begin{verbatim}
Features
(The [Check.icon] means we believe this feature is unique \
 to {\SB} among competing services.)

[[Easy to use Gyazo images]]
 By using together with [Gyazo https://gyazo.com] you can \
 surprisingly paste any image onto the page, and it \
 displays instantly.

[Check.icon] [[Use of an [image] to represent pages]]
 By attaching images to each page, it is easier to discover \
and remember them. Our method allows visual organization to \
happen spontanteously.
\end{verbatim}
}

When we list the URLs of Web pages of
movies and musics on a {\SB} page,
% we can create a hierarchical structure from the list and
% use the Gear interface to find data and browse it.
We can use {\SC} service
for using the Gear interface to select a program from the
list on {\SC} pages, and automatically play it on the browser.

@@

\begin{figure}[H]
% \centerline{\includegraphics[width=40mm,bb=0 0 417 619]{figures/2690db244045aa809a3e2fc2b40ba0a3.png}}
\centerline{\includegraphics[width=30mm,bb=0 0 387 568]{figures/2b97930bf5730fcaf4d9c0adeb9c5f6e.png}}
\caption{A movie list page on {\SB}.}
\label{movielist}
\end{figure}

The raw text of this page is shown below:

{\scriptsize
\begin{verbatim}
Movies
 [https://www.netflix.com/watch/70105600 Gran Torino]
 [https://www.netflix.com/watch/80047616 My Intern]
 [https://www.netflix.com/watch/330201 Breakfast at Tiffany's]
 [https://www.netflix.com/watch/70080178 Heroes]
 [https://www.netflix.com/watch/70174781 Sherlock]
 [https://www.happyon.jp/watch/100048550 Mad Max]
 [https://www.netflix.com/watch/60010351 Flashdance]
 [https://www.netflix.com/watch/80095365 La La Land]
 [https://www.netflix.com/watch/81191988 Don't stop the camera]
 [https://youtube.com/embed/AtZr9g2vwrI?autoplay=1 Fireplace]
\end{verbatim}}

\begin{figure}[H]
% \centerline{\includegraphics[width=80mm,bb=0 0 524 598]{figures/65b01a87b67c9a8e838a047b945f6a77.png}}
\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
\caption{Watching ``Breakfast at Tiffany's''.}
\label{tiffany}
\end{figure}

When we access this {\SB} page from {\SC},
``Gran Trino'' from Netflix automatically starts in the right side of the screen,
just like a TV program starts when we rotate the channel dial of an old television.
When the user pushes the {\down} key twice,
``Breakfast at Tiffarny's'' is selected and
the movie starts at the right side of the screen. (Figure \ref{tiffany})

@@

In one page, we can specify a hierarchical structure by using indentations.
Figure \ref{musiclist} shows a portion of a list of music CDs and
titles by ``Weather Report'' and ``Wes Montgomery'' are shown\footnote{
  Weather Report is the name of a famous Jazz group, and Wes Montgomery is a famous Jazz guitarist.
}.
For example, 
``Black Market'' is the first title in the album ``8:30'' of ``Weather Report'', and
``Scarlet Woman'' follows ``Black Market''.
``Wes Montgomery'' is listed in the same layer as ``Weather Report'', and
the album ``Tequilla'' is listed one level below the level of the name of the artist.

\begin{figure}[H]
% \centerline{\includegraphics[width=40mm,bb=0 0 596 808]{figures/6657544cf60cbf0aea91ba7da0455b90.png}}
\centerline{\includegraphics[width=50mm,bb=0 0 652 926]{figures/d8fe8ff8f3e1bbcb34cf51e268592f8c.png}}
\caption{Music list.}
\label{musiclist}
\end{figure}

The title of this {\SB} page is ``Music'', and 
we can collect Movie page, Music page, and other pages by
listing them in another page (``Top'' page, in this case).

\begin{figure}[H]
% \centerline{\includegraphics[width=40mm,bb=0 0 396 523]{figures/8a8e4d63b75183f1b4d0ed4db733f500.png}}
\centerline{\includegraphics[width=27mm,bb=0 0 262 515]{figures/5a644f357ba6a6b81b011e200019d736.png}}
\caption{Top page.}
\label{top}
\end{figure}

Many pages (Music, Movies, etc.) are listed in the Top page, and
the pages are treated as children pages of the Top page.
By constructing data hierarchically like this,
We can build a very large hierarchical database for watching movies, videos, news, etc.
A hierarchical database with
As many as 100,000 pages can be easily constructed on a {\SB} pages, and
we can select one of the entries only by using only {\up} and {\down} keys,
using the Gear technique described in section \ref{navigation}.

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/blackmarket.png}}
\caption{Playing a music.}
\label{blackmarket}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/blackjack.png}}
\caption{Reading a comic book.}
\label{blackjack}
\end{figure}

Since anybody can edit {\SB} pages and construct the hierarchical data,
people can enjoy creating their own hierarchical database by editing their {\SB} pages.
When someone wants to advertise their works,
he can create his {\SB} pages
and give them to other people so that they can watch the pages.
People can freely include other people's {\SB} pages in their own list
and enjoy all the contents just by using Gear.

@@

The simplest input device for Gear may be keyboards and push buttons.
Gear works pretty comfortably with arrow keys on a PC.
Various HID devices\footnote{
  \tsf{https://en.wikipedia.org/wiki/Human\_interface\_device}
} are available on the market, and
all such devices can be used as an input device for Gear.
For example, a foot switch for turning music score pages\footnote{
  \tsf{https://airturn.com/products/airturn-pedpro}
} can be used as an input device for Gear.
Even a special foot pedal can be used for Gear (Figure \ref{footswitch}).

\begin{figure}[H]
\centerline{\includegraphics[width=40mm,bb=0 0 900 900]{figures/8d4f811f5a0c393acaff304102ba963f.jpg}}
\caption{A foot switch for turning a music score.}
\label{footswitch}
\end{figure}

%
% Good thing is that many keyboard devices are available for personal computers,
% and we can use such devices for using Gear.
% ``Key-repeat'' feature is useful for fast scrolling of the menu.

@@

\begin{figure}[H]
  \centerline{\includegraphics[width=54mm,bb=0 0 514 418]{figures/3c2de63899653056f3c6be835b9aaf43.png}}
\caption{Paddle device for Gear.}
\label{paddle}
\end{figure}

@@

% Keys and pressure sensors can be placed anywhere:
% we tried putting two pressure sensors at the bottom of a chair, and it worked fine.

@@

\begin{figure}[H]
\centerline{\includegraphics[width=54mm,bb=0 0 1324 1095]{figures/7a2c685b930cd30a267f4d564a8079be.png}}
\caption{Using a jog dial.}
\label{jog}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=54mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
\caption{A disk-based device for Gear.}
\label{disk}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=54mm,bb=0 0 1132 1039]{figures/6ff91502ea4f3f3c47840c887148ada9.png}}
\caption{Using a roller.}
\label{roller}
\end{figure}

@@

% Keys and pressure sensors can be placed anywhere:
% we tried putting two pressure sensors at the bottom of a chair, and it worked fine.

\comment{
We tried a lever with two pressure sensors.
モールス用「エレキー」
Puddle

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 1200 799]{figures/d64d2a8e1dddc57f693267f811510f23.jpg}}
\caption{Elekey.}
\label{elekey}
\end{figure}
}

After trying various devices, it became clear that simple buttons or
wheels can be put at anywhere like on the table or under a chair, and
we felt that the integration of furniture and input devices will be
important in the IoT age.
%
If we can install the devices neatly on furniture and beds, people with disabilities can easily use them,

@@

\begin{figure}[H]
\centerline{
%  \includegraphics[width=38mm,bb=0 0 1624 1193]{figures/d663e8556732d40e70e55592ca1f1258.png}
  \includegraphics[width=70mm,bb=0 0 1624 1193]{figures/75007628f75ef1038bd5737e10a728b7.png}
}
\caption{App1: Gear-based application for finding a monorail picture.}
\label{monorailgear}
\end{figure}

@@

\begin{figure}[H]
\centerline{
  \includegraphics[width=70mm,bb=0 0 1596 1116]{figures/325208a6d94c68e4f08e61a67df419c4.png}
}
\caption{App2: using input element.}
\label{monorailinput}
\end{figure}

@@

\begin{figure}[H]
\centerline{
  \includegraphics[width=38mm,bb=0 0 960 593]{figures/6c39f199b341e30ffc28850afbd90a5a.png}
  \includegraphics[width=38mm,bb=0 0 960 593]{figures/de3f0545e0d0d8dfb9708d2420fb5407.png}
}
\caption{Average search time of App1 and App2.}
\label{monorailtime}
\end{figure}

The average time for finding an entry using Gear was 6.84s,
and the average time using standard \ttt{{\textless}input{\textgreater}} was 4.96s.
It takes about 40\% more time than using conventional method.
The standard deviations were 0.71s and 0.93s, respectively.
%
This is a little bit disappointing,
but we are happy to see that
no-click browsing with Gear is not too slower than
conventional methods.

We have also tried using Finder.app for the same data (Figure \ref{noclickfinder}), and
got similar results as App2.

@@

% More conventional visualization techniques like TreeView\footnote{
%   \textsf{http://en.wikipedia.org/wiki/Tree\_view}
% } by replacing 4-way navigation to our approach.

% {\ST} can be adopted to more conventional visualization techniques like
% TreeView\footnote{
%   \textsf{http://en.wikipedia.org/wiki/Tree\_view}
% } by replacing 4-way navigation to our approach.

@@

\begin{figure}[H]
\centerline{
  \includegraphics[width=38mm,bb=0 0 188 188]{figures/treeview.png}
}
\caption{A TreeView example.}
\label{treeview}
\end{figure}

@@

\subsection{Timing control}

@@

Since the idea of Gear interface is so simple,
we have been wondering if the same idea existed in the past.
%
We could not find a research paper on 
navigation techniques based on two keys.
Many key-based navigation techniques are found on patent database,
but we could not find a navigation method based on two keys.
We are almost sure that The Gear interface had never been popular before.

>>>>

\long\def\ttt#1{\texttt{\textbf{\small #1}}}
\long\def\tsf#1{\textsf{\small{#1}}}
\long\def\tit#1{\textit{\small{#1}}}

@@

\author{\IEEEauthorblockN{Toshiyuki Masui}
  \IEEEauthorblockA{
    \textit{Keio University} \\
    \textit{Faculty of Environment and Information Studies}\\
    5322 Endo, Fujisawa, Kanagawa 252-0882 Japan \\
    masui@pitecan.com
  }
}

@@

\begin{abstract}
We introduce a simple interaction technique for finding and browsing
data in a large hierarchical database using only two keys.

Finding a data from a huge hierarchical database takes time
because users should traverse the tree using a mouse or a keyboard,
and click a ``select'' button to check the content.
If the data was not appropriate,
they should go to the next entry and perform the selection task again.

In the past, when only a small number of ``channels'' were available
from broadcast TV stations, users could simply rotate
a television dial to select a channel and watch a program.
We introduce a simple interaction technique called ``\textit{Gear}'',
with which users can select an entry from a large hierarchical database and
browse it instantly, just like we could select a channel and enjoy a program
using old television dials.
\end{abstract}

@@

Huge amount of movies, musics, and other programs are available on the web, but
finding and viewing a program is not easy because
(1) finding a program takes time, and
(2) a ``confirm'' operation (clicking something or typing a key)
is required for viewing the content.
%
The confirm operations was not required on old TVs and radios,
because we could enjoy TV/radio programs
as soon as we rotated a TV channel dial or a tuning dial of the radio.
%
It is always convenient to view the contents of the selected item
as soon as we find it.
We call such viewing style as ``\textbf{\tit{no-click browsing}}''.

We can use no-click browsing on the ``column view'' mode of Finder.app on MacOS.
In the column view mode, 
the contents of the file is shown at the right side of the window
as soon as we select a file in a folder (Figure \ref{noclickfinder}).
When we type an arrow key and select another file,
the contents is shown instantly without a confirm operation.

\begin{figure}[H]
  \centerline{\includegraphics[width=70mm,bb=0 0 839 423]{figures/10d7ca6c55aa93ebcdab799246e4c087.jpg}}
  \caption{No-click browsing on the ``column view'' of Finder.app.}
  \label{noclickfinder}
\end{figure}

@@

It would be better
if we could perform the navigation task using devices that have only two keys.
%
We have developed a new navigation technique called ``{Gear}'' for no-click browsing,
where users can explore a large hierarchical database by using only two keys.

@@

Interaction with Gear is based on the following simple principles.
Two types of operations,
{\up} (up) and {\down} (down), are used for the navigation.

@@

\begin{figure}[H]
  \centerline{\includegraphics[width=55mm,bb=0 0 490 490]{figures/fig1.pdf}}
  \caption{Sample data: shops data of a shopping mall.}
  \label{fig1}
\end{figure}

@@

\begin{figure}[H]
  \begin{minipage}{0.45\hsize}
    \centerline{\includegraphics[width=17mm, bb=0 0 139 157]{figures/fig2.pdf}}
    \caption{Initial display.}
    \label{fig2}
  \end{minipage}
  \begin{minipage}{0.45\hsize}
    \centerline{\includegraphics[width=17mm,bb=0 0 139 157]{figures/fig3.pdf}}
    \caption{Typing {\down}.}
    \label{fig3}
  \end{minipage}
\end{figure}

@@

\begin{figure}[H]
  \begin{minipage}{0.45\hsize}
    \centerline{\includegraphics[width=17mm,bb=0 0 139 157]{figures/fig4.pdf}}
    \caption{Selecting Food/drink.}
    \label{fig4}
  \end{minipage}
  \begin{minipage}{0.45\hsize}
    \centerline{\includegraphics[width=17mm,bb=0 0 139 238]{figures/fig5.pdf}}
    \caption{Selecting Liquor shop.}
    \label{fig5}
  \end{minipage}
\end{figure}

When the user issues {\down} twice here,
\tsf{Fresh grocery} category is selected (Figure \ref{fig6}).
%
If the user keeps issuing {\down}, 
the list will change to Figure \ref{fig8},
without expanding the children of \tsf{Fresh grocery}.

\begin{figure}[H]
  \begin{minipage}{0.45\hsize}
    \centerline{\includegraphics[width=17mm,bb=0 0 139 238]{figures/fig6.pdf}}
    \caption{Selecting Fresh grocery.}
    \label{fig6}
  \end{minipage}
  \begin{minipage}{0.45\hsize}
    \centerline{\includegraphics[width=17mm,bb=0 0 139 157]{figures/fig8.pdf}}
    \caption{Selecting Clothing.}
    \label{fig8}
  \end{minipage}
\end{figure}

If the use stops issuing {\down} at Figure \ref{fig6},
the shops under category \tsf{Fresh grocery} is automatically selected (Figure \ref{fig7}).
%
When the user issues {\up} here, \tsf{Fresh grocery} is selected,
and the shops under \tsf{Fresh grocery} disappears, 
resulting in the same state as Figure \ref{fig6}.
If the user issues {\up} two more times, the display changes to the state
shown in Figure \ref{fig5},
and one more {\up} will set the system to the state of Figure \ref{fig4}.

@@

\begin{figure}[H]
  \begin{minipage}{0.45\hsize}
    \centerline{\includegraphics[width=17mm,bb=0 0 139 292]{figures/fig7.pdf}}
    \caption{Selecting Fish store.}
    \label{fig7}
  \end{minipage}
  \begin{minipage}{0.45\hsize}
    \centerline{\includegraphics[width=17mm,bb=0 0 139 211]{figures/fig9.pdf}}
    \caption{Selecting Shoes store.}
    \label{fig9}
  \end{minipage}
\end{figure}

@@

To prove that Gear is useful for selecting an entry from a
large hierarchical database,
we have developed the ``\tsf{\SC}'' service\footnote{
  \tsf{https://serencast.com/}
}, where users can enjoy movies, musics, and other web services
on the browser with the Gear interface without clicking an entry.
{\SC} is implemented in JavaScript and runs on modern web browsers.
%
{\SC} uses the ``\tsf{\SB}'' wiki service\footnote{
  \tsf{https://Scrapbox.io/}
} for listing the contents of the hierarchical database.
{\SB} is an interactive wiki
system where users can share and edit texts on the web browser,
just like the Google Docs system.

When we list the URLs of Web pages of
movies and musics on a {\SB} page,
we can use {\SC} service
for using the Gear interface to select a program from the
list on {\SB} pages, and automatically play it on the browser.

@@

\comment{
\begin{figure}[H]
  \centerline{\includegraphics[width=30mm,bb=0 0 387 568]{figures/2b97930bf5730fcaf4d9c0adeb9c5f6e.png}}
  \caption{A movie list page on {\SB}.}
  \label{movielist}
\end{figure}
}

\begin{figure}[H]
{\scriptsize
\begin{verbatim}
Movies and videos
 [https://www.netflix.com/watch/70105600 Gran Torino]
 [https://www.netflix.com/watch/80047616 My Intern]
 [https://www.netflix.com/watch/330201 Breakfast at Tiffany's]
 [https://www.netflix.com/watch/70080178 Heroes]
 [https://www.netflix.com/watch/70174781 Sherlock]
 [https://www.happyon.jp/watch/100048550 Mad Max]
 [https://www.netflix.com/watch/60010351 Flashdance]
 [https://www.netflix.com/watch/80095365 La La Land]
 [https://www.netflix.com/watch/81191988 Don't stop the camera]
 [https://youtube.com/embed/AtZr9g2vwrI?autoplay=1 Fireplace]
\end{verbatim}
}
\caption{A movie list page on {\SB}.}
\label{movielist}
\end{figure}

When we access this {\SB} page from {\SC},
``Gran Trino'' from Netflix automatically starts in the right side of the screen,
just like a TV program starts when we rotate the channel dial of an old television.
When the user pushes the {\down} key twice,
``Breakfast at Tiffarny's'' is selected and
the movie starts automatically at the right side of the screen. (Figure \ref{tiffany})

\begin{figure}[H]
  \centerline{\includegraphics[width=65mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
  \caption{Watching ``Breakfast at Tiffany's''.}
  \label{tiffany}
\end{figure}

@@

In one page, we can specify a hierarchical structure by using indentations.
Figure \ref{musiclist} shows a portion of a list of music CDs and
titles by ``Weather Report'' and ``Wes Montgomery'' are shown\footnote{
  Weather Report is the name of a famous Jazz group, and Wes Montgomery is a famous Jazz guitarist.
}.
For example, 
``Black Market'' is the first title in the album ``8:30'' of ``Weather Report'', and
``Scarlet Woman'' follows ``Black Market''.
``Wes Montgomery'' is listed in the same layer as ``Weather Report'', and
the album ``Tequilla'' is listed one level below the level of the name of the artist.
%
The title of {\SB} page shown in Figure \ref{musiclist} is ``Music'', and 
we can collect Movie page, Music page, and other pages by
listing them in another page (``Top'' page) shown in Figure \ref{top}.

\begin{figure}[H]
 \begin{minipage}{0.45\hsize}
  \centerline{\includegraphics[width=30mm,bb=0 0 652 926]{figures/d8fe8ff8f3e1bbcb34cf51e268592f8c.png}}
  \caption{Music list.}
  \label{musiclist}
 \end{minipage}
 \begin{minipage}{0.45\hsize}
  \centerline{\includegraphics[width=22mm,bb=0 0 262 515]{figures/5a644f357ba6a6b81b011e200019d736.png}}
  \caption{Top page.}
  \label{top}
 \end{minipage}
\end{figure}

Many {\SB} pages (Music, Movies, etc.) are listed in the Top page, and
the pages are treated as children pages of the Top page.
By constructing data hierarchically like this,
We can build a very large hierarchical database for watching movies, videos, news, etc.
A hierarchical database with
As many as 100,000 pages can be easily constructed on {\SB}, and
we can select one of the entries only by using {\up} and {\down} keys,
with the Gear technique described in section \ref{navigation}.

\comment{
\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/blackmarket.png}}
\caption{Playing a music.}
\label{blackmarket}
\end{figure}

\begin{figure}[H]
\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/blackjack.png}}
\caption{Reading a comic book.}
\label{blackjack}
\end{figure}
}

Since anybody can edit {\SB} pages and construct the hierarchical data,
people can enjoy creating their own database by editing their {\SB} pages.
When someone wants to advertise their works,
he can create his {\SB} pages
and give them to other people so that they can watch the pages.
People can freely include other people's {\SB} pages in their own list
and enjoy all the contents just by using Gear.

@@

The simplest input device for Gear may be keyboards and push buttons.
Gear works pretty comfortably with arrow keys on a PC.
Various HID devices\footnote{
  \tsf{https://en.wikipedia.org/wiki/Human\_interface\_device}
} are available on the market, and
all such devices can be used as an input device for Gear.

@@

\begin{figure}[H]
  \centerline{\includegraphics[width=38mm,bb=0 0 514 418]{figures/3c2de63899653056f3c6be835b9aaf43.png}}
  \caption{Paddle device for Gear.}
  \label{paddle}
\end{figure}

@@

@@

\begin{figure}[H]
  \begin{minipage}{0.49\hsize}
    \centerline{\includegraphics[width=38mm,bb=0 0 1324 1095]{figures/7a2c685b930cd30a267f4d564a8079be.png}}
    \caption{Using a jog dial.}
    \label{jog}
  \end{minipage}
  \begin{minipage}{0.49\hsize}
    \centerline{\includegraphics[width=38mm,bb=0 0 362 354]{figures/ff2d18e66f9a4655dbb5e22e0bb9a0ae.png}}
    \caption{A disk-based device for Gear.}
    \label{disk}
  \end{minipage}
\end{figure}

@@

\begin{figure}[H]
  \centerline{\includegraphics[width=38mm,bb=0 0 1132 1039]{figures/6ff91502ea4f3f3c47840c887148ada9.png}}
  \caption{Using a roller.}
  \label{roller}
\end{figure}

@@

After trying various devices, it became clear that simple buttons or
wheels can be put at anywhere like on the table or under a chair, and
we felt that the integration of furniture and input devices will be
important in the IoT age\cite{10.1145/2494091.2497326}.
%
If we can install the devices neatly on furniture and beds,
people with disabilities can easily use them.

@@

@@

\begin{figure}[H]
  \begin{minipage}{0.49\hsize}
    \centerline{\includegraphics[width=40mm,bb=0 0 1624 1193]{figures/75007628f75ef1038bd5737e10a728b7.png}}
    \caption{App1: Gear-based application for finding a monorail picture.}
    \label{monorailgear}
  \end{minipage}
  \begin{minipage}{0.49\hsize}
    \centerline{\includegraphics[width=40mm,bb=0 0 1596 1116]{figures/325208a6d94c68e4f08e61a67df419c4.png}}
    \caption{App2: using input element.}
    \label{monorailinput}
  \end{minipage}
\end{figure}

@@

\begin{figure}[H]
\centerline{
  \includegraphics[width=39mm,bb=0 0 960 593]{figures/6c39f199b341e30ffc28850afbd90a5a.png}
  \includegraphics[width=39mm,bb=0 0 960 593]{figures/de3f0545e0d0d8dfb9708d2420fb5407.png}
}
\caption{Average search time of App1 and App2.}
\label{monorailtime}
\end{figure}

The average time for finding an entry using Gear was 6.84s,
and the average time using standard \ttt{{\textless}input{\textgreater}} was 4.96s.
It takes about 40\% longer than using conventional method.
The standard deviations were 0.71s and 0.93s, respectively.
%
This is a little bit disappointing,
but we are happy to see that
no-click browsing with Gear is not too slower than
conventional methods.
%
We have also tried using Finder.app for the same data (Figure \ref{noclickfinder}), and
got similar results as App2.

@@

@@

\comment{
  \begin{figure}[H]
    \centerline{
      \includegraphics[width=38mm,bb=0 0 188 188]{figures/treeview.png}
    }
    \caption{A TreeView example.}
    \label{treeview}
  \end{figure}
}

@@

\comment{
\subsection{Timing control}

@@

Since the idea of Gear interface is so simple,
we have been wondering if the same idea existed in the past.
%
We could not find a research paper on 
navigation techniques based on two keys.
Many key-based navigation techniques are found on patent database,
but we could not find a navigation method based on two keys.
We are almost sure that The Gear interface had never been popular before.
}
